% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm]{acmart}

\usepackage{graphicx}
\usepackage{balance}        % for  \balance command ON LAST PAGE  (only there!)
\usepackage{hyperref}       % hyperlinks
\usepackage{graphicx}
\usepackage{comment}
\usepackage{multicol}
\usepackage{framed}
\usepackage{subcaption}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{minted}
\usepackage{multicol}

% \setlength{\intextsep}{10pt plus 2pt minus 3pt}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{10.14778/3476311.3476381}
\newcommand\vldbpages{3240-3252}
% issue-specific
\newcommand\vldbvolume{14}
\newcommand\vldbissue{12}
\newcommand\vldbyear{2021}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle}
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{https://github.com/luisremis/visual_storm/tree/master/yfcc100m}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{empty}

\begin{document}
\title{Using VDMS to Index and Search 100M Images}

%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
\author{Luis Remis}
\affiliation{%
  \institution{ApertureData}
  \titlenote{Luis Remis was a Research Scientist at Intel Labs until late 2019. Most of this work was done while at Intel Labs.}
}
\email{luis@aperturedata.io}

\author{Chaunt\'e W. Lacewell}
\affiliation{%
  \institution{Intel Labs}
}
\email{chaunte.w.lacewell@intel.com}

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Data scientists spend most of their time dealing with data preparation,
rather than doing what they know best:
build machine learning models and algorithms to solve previously unsolvable problems.
In this paper, we describe the Visual Data Management System (VDMS),
and demonstrate how it can be used to simplify the data preparation process
and consequently gain in efficiency simply because
we are using a system designed for the job.
To demonstrate this, we use one of the largest available
public datasets (YFCC100M),
with 100 million images and videos, plus additional data including
machine-generated tags, for a total of about $\sim$12TB of data.
VDMS differs from existing data management systems
due to its focus on supporting machine learning and
data analytics pipelines that rely on images, videos, and feature vectors,
treating these as first class citizens.
We demonstrate how VDMS outperforms well-known and widely used
systems for data management by up to $\sim$364x, with
an average improvement of about 85x for our use-cases, and particularly at scale,
for a \textit{image search} engine implementation.
At the same time, VDMS simplifies the process of data preparation and data access,
and provides functionalities non-existent in alternative options.
\end{abstract}

\maketitle

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\pagestyle{\vldbpagestyle}
\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\endgroup
\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150-8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\ifdefempty{\vldbavailabilityurl}{}{
\vspace{.3cm}
\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
\endgroup
}
%%% VLDB block end %%%

\input{intro}
\input{design}
\input{eval}
\input{conclusion}
\input{futurework}
\input{acks}

\clearpage
% \begin{multicols}{2}
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{ACM-Reference-Format}
\bibliography{vdms-vldb2021}
\input{legal}
% \end{multicols}{2}
% \balance

\end{document}
\endinput
